DATA 621 - Business Analytics and Data Mining

### 2020-11-20 HW5/HW5-Draft.Rmd
Finish train/test split. Now going to build my set of models.

The numeric predictors all look to be basically symmetrical, but non-Gaussian in
that there is a strong spike near the median, but the tails on either side are
thicker than would be for a normal distribution with that low of a standard
deviation.

@@

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
```{r loadData}
```
```{r missingVal}
```
```{r statsN}
```
```{r graphsD}
```
```{r graphsH}
```
```{r corrgram}
```
```{r dataClean}
```
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r m2clean}
```
```{r m3clean}
```
```{r model1DummyFreq}
```
```{r model1RunFreq}
```
```{r model1DummySev}
```
```{r model1RunSev}
```
```{r model2RunFreq}
```
```{r model2RunSev}
```
```{r model3RunBaseLog}
```
```{r model3RunFreq}
```
```{r model3RunBaseLin}
```
```{r model3RunSev}
```
```{r setUpCompTables}
```
```{r validateM1F}
```
```{r validateM1S}
```
```{r validateM2F}
```
```{r validateM2S}
```
```{r validateM3F}
```
```{r validateM3S}
```
```{r freqComp}
```
```{r sevComp}
```
```{r badSev}
```
```{r evalProcessClean}
```
```{r evalPredictFreq}
```
```{r evalPredictSev}
```

>>>>

The numeric predictors all look to be basically symmetrical, but non-Gaussian in
that there is a strong spike near the median, but the tails on either side are
thicker than would be for a normal distribution with that low of a standard
deviation. This is also why a boxplot would be a poor graphical indicator, as
the spike at the medians would lead to a compressed inter-quartile range and a
plethora of outliers.

@@

# DATA PREPARATION
First, preparation necessary for all the models equally will be performed. The
subsequent imputation and feature generation, if necessary will be discussed in
a separate subsection for each modeler.

## Training & Testing Split
All the models will be trained on the same approximately 70% of the training
set, reserving 30% for validation of which model to select for the count
estimation on the supplied evaluation set.

```{r trainTestSplit}
# Create training and testing split
set.seed(1004)
trnIDX <- createDataPartition(DT$TARGET, p = 0.7)
trnX <- DT[trnIDX$Resample1, ]
tstX <- DT[!trnIDX$Resample1, ]
```

# Modeler # 1
## Missing Data
The missing daya

# SELECT MODELS
## Model Selection Criteria
We will look at RMSE and AIC as our metrics and select the model which performs
best on both, Ties will be broken by \(R^2\).

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
```{r loadData}
```
```{r missingVal}
```
```{r statsN}
```
```{r graphsD}
```
```{r graphsH}
```
```{r corrgram}
```
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r m2clean}
```
```{r m3clean}
```
```{r model1DummyFreq}
```
```{r model1RunFreq}
```
```{r model1DummySev}
```
```{r model1RunSev}
```
```{r model2RunFreq}
```
```{r model2RunSev}
```
```{r model3RunBaseLog}
```
```{r model3RunFreq}
```
```{r model3RunBaseLin}
```
```{r model3RunSev}
```
```{r setUpCompTables}
```
```{r validateM1F}
```
```{r validateM1S}
```
```{r validateM2F}
```
```{r validateM2S}
```
```{r validateM3F}
```
```{r validateM3S}
```
```{r freqComp}
```
```{r sevComp}
```
```{r badSev}
```
```{r evalProcessClean}
```
```{r evalPredictFreq}
```
```{r evalPredictSev}
```
